Lactate transport inhibition therapeutically reprograms fibroblast

### 2024-02-15 manuscript/manuscript.qmd
add mice phenotype figures

# ensure figures are up-to-date
targets::tar_load(
  c(
    fig01,
    fig02,
    fig03,
    fig04,
    fig05,
    fig06,
    fig07,
    # fig10,
    # fig11,
    # resources_table,
    NULL
  )
)
```

@@

>>>>

# ensure figures are up-to-date
targets::tar_load(
  c(
    fig01,
    fig02,
    fig03,
    fig04,
    fig05,
    fig06,
    fig07,
    fig08, 
    # fig10,
    # fig11,
    # resources_table,
    NULL
  )
)
```

@@

## MCT inhibition decreases experimental pulmonary fibrosis

Based on our *in vitro* data suggesting an anti-fibrotic effect of lactate transporter inhibition, we next tested the efficacy of MCT inhibitors in the bleomycin-induced mouse model of pulmonary fibrosis. Mice received 1.2 U/kg bleomycin by intratracheal administration. After seven days, the animals began treatment with AZD3965 (100 mg/kg twice daily) or VB124 (30 mg/kg once daily) or vehicle by oral gavage (**Figure 8A**). We anticipated that dual inhibition would likely be toxic *in vivo* and did not assess the combination of inhibitors. Compared to vehicle, mice treated with VB124 had increased weight recovery 21 days after bleomycin administration (**Supplemental Figure 8**). Lung mechanics were improved by ~ 50% of baseline compared to vehicle controls following 14 days of MCT inhibitor treatment (**Figure 8B-C**). Consistent with improved elastance and compliance measures, histologic fibrosis severity assessed by Ashcroft scoring [@ashcroft1988] also improved.
